---
title: "Case study"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
library(visNetwork)
library(networkD3)
```

```{r, eval=F, echo = F}

## Load library
# ```{r, message=FALSE}
library(igraph)
library(visNetwork)
library(networkD3)
#```

<br>

## Graph object
#```{r}
df = read.table("./data/data1.tsv", header = F, sep="\t")
g = graph_from_data_frame(df)
#```

<br>

#```{r, eval=FALSE}
genes = V(g)$name
deg = degree(g)
bet = betweenness(g)
clos = closeness(g)
eigen = eigen_centrality(g)$vector
res = data.frame(genes = genes, degree = deg[genes], betweenness = bet[genes], closeness = clos[genes], eigen = eigen[genes])
#```

#```{r, eval=FALSE}
ggplot(res,aes(x=genes, y=degree))+geom_point()
#```

## Further study

#https://datascienceplus.com/network-analysis-of-game-of-thrones/

```

## Download data
```{r}
nodes <- jsonlite::fromJSON("https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/nodes_miserables.json")

edges <- jsonlite::fromJSON("https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/edges_miserables.json")

g = graph_from_data_frame(d = edges, directed = T, vertices = nodes)
```

<br><br>

## Answer the following questions

1. How many nodes and edges
2. Print the graph object and try to understand the summary shown
3. What are the different node attributes


