---
title: "visNetwork"
output: pdf_document
always_allow_html: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(echo = TRUE)
```

## Load library
```{r, message=FALSE}
library(igraph)
library(visNetwork)
library(networkD3)
library(dplyr)
```

## Graph object
```{r}
df = read.table("./data/data.tsv", header = T)
veccol = c(rep("pink",5), rep("light blue",6))
g = graph_from_data_frame(df)
net = g
```

## Create nodes and edges data frames
visNetwork needs at least two pieces of information :

* a nodes data.frame, with id column

* an edges data.frame, with from and to columns, which make the link with id


```{r}
nodes = data.frame(id = V(g)$name)
nodes$label = nodes$id
edges = data.frame(get.edgelist(g))
colnames(edges) = c('from','to')
head(nodes)
head(edges)
```
## Visualize

```{r}
visNetwork(nodes = nodes, edges = edges)
```

## visNodes

### Shape, title, borderWidth
```{r}
visNetwork(nodes, edges) %>% visNodes(color = "red",shape = "square", title = "Gene Fusion Network", borderWidth = 3)
```

### Change color properties with multiple parameters
```{r}
visNetwork(nodes, edges) %>% 
  visNodes(color = list(
    background = "red", 
    border = "blue", 
    highlight = "yellow"))
```

### Add hover property
```{r}
visNetwork(nodes, edges) %>%
  visNodes(color = list(hover = "green")) %>%
  visInteraction(hover = TRUE)
```

### Add shadow
```{r}
visNetwork(nodes, edges) %>% visNodes(shadow = TRUE)
visNetwork(nodes, edges) %>% visNodes(shadow = list(enabled = TRUE, size = 50))
```

## visEdges

### Arrows
```{r}
visNetwork(nodes, edges) %>% visEdges(arrows = 'from')
visNetwork(nodes, edges) %>% visEdges(arrows = 'to')
visNetwork(nodes, edges) %>% visEdges(arrows = 'middle')
visNetwork(nodes, edges) %>% visEdges(arrows = 'to, from')
visNetwork(nodes, edges) %>% visEdges(arrows = 'to, from, middle')
```

### Smooth

Boolean | named list. Default to named list. When true, the edge is drawn as a dynamic quadratic bezier curve. The drawing of these curves takes longer than that of straight curves but it looks better.
 
* "enabled" : Boolean. Default to true. Toggle smooth curves on and off. This is an optional option. If any of the other properties in this object are set, this option will be set to true.

* "type" : String. Default to 'dynamic'. Possible options: 'dynamic', 'continuous', 'discrete', 'diagonalCross', 'straightCross', 'horizontal', 'vertical', 'curvedCW', 'curvedCCW', 'cubicBezier'.

* "roundness" : Number. Default to 0.5. Accepted range: 0 .. 1.0. This parameter tweaks the roundness of the smooth curves for all types EXCEPT dynamic.

* "forceDirection" : String or Boolean. Default to false. Accepted options: ['horizontal', 'vertical', 'none']. This options is only used with the cubicBezier curves. When true, horizontal is chosen, when false, the direction that is larger (x distance between nodes vs y distance between nodes) is used. If the x distance is larger, horizontal. This is ment to be used with hierarchical layouts.

```{r}
visNetwork(nodes, edges) %>% visEdges(smooth = FALSE)

visNetwork(nodes, edges) %>% 
  visEdges(smooth = 
             list(
               enabled = TRUE, 
               type = "diagonalCross"))
```

### width
```{r}
visNetwork(nodes, edges) %>% visEdges(width = 10)
```

### color edges
```{r}
visNetwork(nodes, edges) %>% visEdges(color = "red")

visNetwork(nodes, edges) %>% visEdges(color = list(color = "red", highlight = "yellow"))

visNetwork(nodes, edges) %>% visEdges(color = list(hover = "green")) %>%
 visInteraction(hover = TRUE)
```

## shadow
```{r}
visNetwork(nodes, edges) %>% visEdges(shadow = TRUE)
visNetwork(nodes, edges) %>% visEdges(shadow = list(enabled = TRUE, size = 5))
```

### dashes
globally
```{r}
visNetwork(nodes, edges) %>% visEdges(dashes = TRUE)
```

## Group nodes
```{r}
nodes$group = c(rep("a",6),rep("b",5))
head(nodes)

```

## Color nodes by groups
```{r}
visNetwork(nodes = nodes, edges = edges) %>% visOptions(selectedBy = "group")
```

## Collapse / Uncollapse Nodes
```{r}
visNetwork(nodes = nodes, edges = edges) %>% visOptions(collapse = TRUE) 
```

## Highlight nearest
```{r}
visNetwork(nodes = nodes, edges = edges) %>% visOptions(highlightNearest = TRUE)
visNetwork(nodes = nodes, edges = edges) %>% visOptions(highlightNearest = list(enabled = T, degree = 2, hover = T) )
```



## Legends
```{r}
# default, on group
visNetwork(nodes, edges, width = "100%") %>%
  visGroups(groupname = "a", color = "red") %>%
  visGroups(groupname = "b", color = "gold") %>%
  visLegend()
```

### Placement and titles
```{r}
visNetwork(nodes, edges, width = "100%") %>%
  visGroups(groupname = "a", color = "red") %>%
  visGroups(groupname = "b", color = "gold") %>%
visLegend(width = 0.1, position = "right", main = "Group")
```


## Another example
```{r}
nodes1 <- jsonlite::fromJSON("https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/nodes_miserables.json")

edges1 <- jsonlite::fromJSON("https://raw.githubusercontent.com/datastorm-open/datastorm-open.github.io/master/visNetwork/data/edges_miserables.json")


visNetwork(nodes1, edges1, height = "700px", width = "100%") %>%
  visOptions(selectedBy = "group", 
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visPhysics(stabilization = FALSE)
```

